
# Variables from the Multi-scale Terrestrial Model Intercomparison Project

```{r}
library(dplyr)
data(mstmip_vars, package = "PEcAn.utils")
data(mstmip_local, package = "PEcAn.utils")

pecan_mstmip_vars <- data.frame(rbind(
  mstmip_vars %>% 
    select(Variable.Name, Long.name, Units, Category),
  mstmip_local %>% 
    select(Variable.Name, Long.name, Units, Category)))

rownames(pecan_mstmip_vars)<-NULL
knitr::kable(pecan_mstmip_vars)

mstmip_vars %>% 
    select(Variable.Name, Long.name, Units, Category, var_type) %>% knitr::kable()
```


## PEcAn output following MsTMIP Standard / 

Can be adapted for Any raster data. Uses NetCDF-4, which is a wrapper for HDF5.

Note: 'chunking' indicates these are time series chunks, so it is fast to read in the time dimension, slower for a short time interval over a larger spatial dimesion.

```{r}
library(ncdf4)
miscanthus_preidction.nc <- nc_open("~/Box Sync/terraref/reference-data/samples/PEcAn/2009.nc")
knitr::kable(print(miscanthus_preidction.nc))

```

## Example

```{r}
library(PEcAn.data.atmosphere)

lai <- ncvar_get(miscanthus_preidction.nc, "LAI")


basetime.string <- ncatt_get(miscanthus_preidction.nc, "time", "units")$value
basetime.string
days_since_basetime.idx <- ncvar_get(miscanthus_preidction.nc, "time")

date <- ymd("1700-01-01") + hours(ud.convert(time.idx, "days", "hours"))


library(ggplot2)
library(ggthemes)
theme_set(theme_tufte())
ggplot() + 
  geom_line(aes(date, lai)) + 
  ylab("Leaf Area Index (m2/m2)" ) + xlab("Date")


vars <- list("LAI", "RootBiom", "Evap", "TVeg")
output <- lapply(vars, function(x) ncvar_get(miscanthus_preidction.nc, x))
names(output) <- vars


for(var in vars){
    print(ggplot() + geom_line(aes(date, output[[var]])) + ylab(var) + xlab("Date"))
} 



```

# References

* Bob Cook
* ORNL DAAC repository
* mstmipsyntesis.pbworks.com
* Annual Reviews paper
* PEcAn Project